### 2021-04-02 Chapter-4/Chapter-4.tex
add figures
Updates from Overleaf

\vspace{3pt}
\textbf{Min Entropy.}
As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$, 
with the definition, min-entropy equals to
\begin{align*}
    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
\end{align*}

@@

 \begin{figure}[h!]
    \vspace*{-5pt}
    \centering
    \begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
\vspace*{-10pt}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\vspace*{-5pt}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/RA.pdf}
\vspace*{-6pt}
    \caption{The gap between the real attack and previous models}\label{fig:gap}
\end{figure}

\subsection{Theoretical Analysis \textbf{(Solution to Challege C1)}}
Now we present our metric to quantify the amount of leaked information from
dynamic analysis.

@@

            %For example, if the program has $2$ input whose size is 
            %one byte, the whole search space is a $256^2$ cube. If we want
            %the sampling distance between each point equals to $d$, we need
            %$256^2d$ points. If the program has $10$ byte input, we need
            %$256^{10}d$ points if we still we want the sampling distance equals
            %to $d$.

      \item The number of satisfying assignments could be exponentially small.
            According to Chernoff bound, we need exponentially many samples to
            get a tight bound. 
            %On an extreme situation, if the constraint only
            %has one unique satisfying solution, the simple Monte Carlo method
            %cannot find the satisfying assignment even after sampling many
            %points.
\end{enumerate}

@@

%% We apply the following
%% algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
%% $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.

@@

After we split those constraints into several small constraints, we count the
number of solutions for each constraint. Even though the dimension has been
significantly reduced by the previous step, this is still a \#P problem. 
%For our
%project, we apply the approximate counting instead of exact counting for two
%reasons. First, we do not need to have a very precise result of the exact number
%of total solutions since the information is defined with a logarithmic function.
%We do not need to distinguish between constraints having $10^{10}$ or $10^{10} +
%10$ solutions; they are very close to after taking logarithmic. Second, the
%precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
%search, have difficulty scaling up to large problem sizes.

@@

%% the algorithm
%\IncMargin{1em}
%\begin{algorithm}
%\SetAlgoLined
%\DontPrintSemicolon

>>>>

\textbf{Min Entropy.}
As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$, 
with the definition, min-entropy equals to
\begin{align*}
    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
\end{align*}

@@

 \begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
\vspace*{-10pt}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
    \caption{The gap between the real attack and previous models}\label{fig:gap}
\end{figure}

\subsection{Theoretical Analysis}
Now we present our metric to quantify the amount of leaked information from
dynamic analysis.

@@

            For example, if the program has $2$ input whose size is 
            one byte, the whole search space is a $256^2$ cube. If we want
            the sampling distance between each point equals to $d$, we need
            $256^2d$ points. If the program has $10$ byte input, we need
            $256^{10}d$ points if we still we want the sampling distance equals
            to $d$.

      \item The number of satisfying assignments could be exponentially small.
            According to Chernoff bound, we need exponentially many samples to
            get a tight bound. 
            On an extreme situation, if the constraint only
            has one unique satisfying solution, the simple Monte Carlo method
            cannot find the satisfying assignment even after sampling many
            points.
\end{enumerate}

@@

We apply the following
algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
$c_t(\addr{1},\addr{2},\ldots,\addr{n})$.

\IncMargin{1em}
\begin{algorithm}[h]\small
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
    \For{$i\leftarrow 2$ \KwTo $n$}
    {
        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
        \For{$g_{i} \in G$}
        {
            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
            \If{$S \neq \emptyset$}
            {
                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
                \textbf{continue} \;
            }
            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
        }
    }
    \caption{The Maximum Independent Partition}
    \label{algo:max-inde}
\end{algorithm}
\DecMargin{1em}

@@

After we split those constraints into several small constraints, we count the
number of solutions for each constraint. Even though the dimension has been
significantly reduced by the previous step, this is still a \#P problem. 
For our
project, we apply the approximate counting instead of exact counting for two
reasons. First, we do not need to have a very precise result of the exact number of total solutions since the information is defined with a logarithmic function.
We do not need to distinguish between constraints having $10^{10}$ or $10^{10} 
10$ solutions; they are very close to after taking logarithmic. Second, the
precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
search, have difficulty scaling up to large problem sizes.

@@

\IncMargin{1em}
\begin{algorithm}\small
    \SetAlgoLined
    \DontPrintSemicolon

    \KwIn{{The constraint $g_{i}= c_{i_1} \land c_{i_2}
                    \land \ldots \land c_{i_m}$}}
    \KwOut{{The number of assignments that satisfy $g_{i}$ $|K_{g_{i}}|$}}

    $n$: the number of sampling times \;
    $S_{c_i}$: the set contains input variables for $c_{i}$ \;
    $n_{s}$: the number of satisfying assignments \;
    $N_{c_t}$: the set contains all solution for $c_t$ \;
    $r$: times of reducing $g$\;
    $k$: the input variable \;
    $R$: a function that produces a random point from $S_{c_i}$\;
    %$\#k$: the satisfying number of k \fixme{this number is not used syntactically} \;
    %Initialization: \;
    $r$ $\leftarrow$ $1$,
    $n$ $\leftarrow$ $0$ \;
    \For{$t$ $\leftarrow$ $1$ \KwTo $m$} {
        $S_{c_t}$ $\leftarrow$ $\pi(c_t)$ \;
        \If{$|S_{c_t}| = 1$}
        {
            $N_{c_t}$ $\leftarrow$ Compute all solutions of $c_i$ \;
            $N_{c_t} = \{n_1, \ldots, n_m\},\ S_{c_t} = \{k\}  $ \;
            $g_{i} = $ $g_i(k=n_1) \land \ldots \land g_i(k=n_m)$ \;
            $r \leftarrow r+1$ \;

        }
    }
    \While{$n \leq \frac{8p}{1-p}$} {
        $S_{g_i}$ $\leftarrow$ $\pi(g_i)$ \;
        $v \leftarrow R(S_{g_i})$ 
        \If{$v$ satisfies $g_i$}
        {
           $n_s \leftarrow n_s + 1$
        }
        $n \leftarrow n +1,\ p = \frac{n_s}{n}$
    }

    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
    \caption{Multiple Step Monte Carlo Sampling}
\end{algorithm}
\DecMargin{1em}
%% the algorithm
%\IncMargin{1em}
%\begin{algorithm}
%\SetAlgoLined
%\DontPrintSemicolon
